%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\usepackage{xifthen}
\usepackage{multicol}


\renewcommand{\subsection}[1]{
  \par\vspace{\parskip}
  {%
    \Large\headingfont\color{headercolor} #1%
  }
  \par\vspace{\parskip}
}
\renewcommand{\subsubsection}[1]{
  \par\vspace{\parskip}
  {%
    \large\headingfont\color{headercolor} #1%
  }
  \par\vspace{\parskip}
}

\newcommand{\ifequals}[3]{\ifthenelse{\equal{#1}{#2}}{#3}{}}
\newcommand{\case}[2]{#1 #2} % Dummy, so \renewcommand has something to overwrite...
\newenvironment{switch}[1]{\renewcommand{\case}{\ifequals{#1}}}{}
\newcommand{\skill}[2]{
  \makebox[2.7cm][l]{#1}%
  \begin{switch}{#2}%
    \case{1}{~~$\ast$\\}%
    \case{2}{~~$\ast\ast$\\}%
    \case{3}{~~$\ast\ast$$\ast$\\}%
    \case{4}{~~$\ast\ast$$\ast\ast$\\}%
  \end{switch}
}

\newenvironment{skillgroup}[1]
{\subsubsection{#1}
}{}



\begin{document}

\header{Daan Wendelen}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Personal}
Nationality: Belgian
Birth: 1990 - 10 - 16
Driving license: B
~
Ambachtstraat 17A
3530 Helchteren
Belgium
~
+32 471 46 08 68
\href{mailto:daanwendelen@gmail.com}{daanwendelen\\@gmail.com}
%\href{http://www.smith.com}{http://www.smith.com}
%\href{http://facebook.com/johnsmith}{fb://jsmith}
~
Nickname: Xtrit
\section{Languages}
\textbf{Dutch}\\Native
~
\textbf{English}\\C1
~
\textbf{Swedish}\\B1
\section{Software\\Engineering}
\begin{tabular}{r l}
Java (7, 8) & ~~$\ast\ast$$\ast\ast$
Scala & ~~$\ast\ast$
Cassandra & ~~$\ast\ast$
Kafka & ~~$\ast\ast$
Zookeeper & ~~$\ast\ast$
Git & ~~$\ast\ast$$\ast$
Jenkins & ~~$\ast\ast$
IntelliJ & ~~$\ast\ast$
Gradle & ~~$\ast\ast$
Scrum & ~~$\ast\ast$

{\scriptsize (more on the next page)}&
\end{tabular}
~
{\tiny \begin{tabular}{r p{2.5cm}}
$\ast$ ~~& Limited, need to work under
& ~~supervission
$\ast\ast$ ~~& Autonomy on simple tasks, need
& ~~couching for complex tasks
$\ast\ast$$\ast$ ~~& Autonomy on complex tasks
$\ast\ast$$\ast\ast$ ~~& Can lead, coach, supervise
& ~~compex tasks
\end{tabular}
~}
\end{aside}

\section{Working experience}
\begin{entrylist}
\entry
{2014--now~~~}
{Software engineer}
{Cegeka}
{I am currently working as a Java developer in an agile scrum team. We work on the v-consult project for our customer Viollier. v-consult is an online platform where the doctors can order medical tests for their patients.
As a developer, it is my responsibility to implement the features that are demanded by Viollier. Every month we release a new version of the software with just a few clicks.}

\end{entrylist}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2012--2015~}
{Master of Engineering: Computer Science}
{KU Leuven}
{Specialisation: Distributed Systems\\
~}


%------------------------------------------------
\entry
{2009--2012~}
{Bachelor of Science in Informatics}
{KU Leuven}
{~}

\entry
{2008--2009~}
{Bachelor of Engineering}
{KU Leuven}
{Discontinued due to reorientation}
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Extracurricular activities}

\begin{entrylist}
%------------------------------------------------
\entry
{2014--2014~}
{Software developer}
{Vlaamse Technische Kring Leuven}
{VTK is the student union of the Engineering Faculty with a turnover of 1,5M EUR. My main task was to develop new software. I also provided technical support concerning components I developed or components of which I have an extensive knowledge.
I was also a member of VTK’s board.\\
~}


\entry
{2012--2014~}
{Treasurer fakbar}
{Vlaamse Technische Kring Leuven}
{A fakbar is a place where students can come together in the evening. It has a turnover of 65K EUR. It was my responsibility to ensure that the fakbar remained financially healthy.\\
~}


\entry
{2012--2014~}
{Fakbar reponsible}
{Vlaamse Technische Kring Leuven}
{I was one evening a week responsible for everything that happened in the fakbar. It was also my job to guide and coordinate the volunteers that worked in the fakbar.\\
~}


\entry
{2011--now}
{Providing client support / Software developer}
{Student IT}
{Student IT is an organisation that provides IT services to student unions that do not have the expertise to do it themselves. One of the services we provide is a platform
where the students can order their books. It is used by 5000 active users.
I provide support for the customers and I occasionally develop new software.}

%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{Professional:} Distributed systems, computer graphics,  neural networks\\
\textbf{Personal:} Videogames, logical puzzles, watching series, listening to music

\newpage
\addtolength{\oddsidemargin}{-1.7cm}
\addtolength{\evensidemargin}{-1.7cm}

\section{Software engineering skills}
~\\
\subsection{Back-end}
\begin{multicols}{3}
\begin{skillgroup}{Frameworks}
\skill{Spring MVC}{3}
\skill{Spring Context}{3}
\skill{Spring Boot}{2}
\skill{String Data}{2}
\skill{Axon}{3}
\skill{Hibernate}{2}
\end{skillgroup}

\begin{skillgroup}{Languages}
\skill{Java (7, 8)}{4}
\skill{Scala}{2}
~\\
~\\
\end{skillgroup}

\begin{skillgroup}{Infrastructure}
\skill{Cassandra}{2}
\skill{Couchbase}{2}
\skill{Kafka}{2}
\skill{Zookeeper}{2}
\skill{Hazelcast}{2}
\skill{ActiveMQ}{2}
\end{skillgroup}

\begin{skillgroup}{Software design}
\skill{CQRS}{3}
\skill{Event Sourcing}{3}
\skill{Reactive Prog.}{3}
\skill{DDD}{2}
\end{skillgroup}

\begin{skillgroup}{Testing}
\skill{JUnit}{3}
\skill{Mockito}{2}
\skill{JMockit}{2}
\skill{AssertJ}{2}
\skill{JBehave}{2}
~\\
\end{skillgroup}

\begin{skillgroup}{Web technology}
\skill{REST}{3}
\skill{Websocket}{2}
\skill{JWT}{2}
\skill{Servlet}{2}
\end{skillgroup}
\end{multicols}


\subsection{General}
\begin{multicols}{3}
\begin{skillgroup}{Dev. tools}
\skill{IntelliJ}{2}
\skill{Eclipse}{2}
\skill{Visual Studio}{1}
\skill{Git}{3}
\skill{SVN}{2}
\skill{Gradle}{2}
\skill{Maven}{2}
\end{skillgroup}

\begin{skillgroup}{Deployment}
\skill{Jenkins}{3}
\skill{Rundeck}{2}
\skill{Docker}{2}
\skill{Netscaler}{2}
\skill{Artifactory}{2}
\skill{.deb packaging}{2}
\skill{.rpm packaging}{2}
\end{skillgroup}

\begin{skillgroup}{Processes}
\skill{Scrum}{2}
\skill{XP}{2}
\skill{Cont. Integration}{2}
\skill{Cont. Delivery}{2}
\skill{Test Driven Dev.}{2}
~\\
~\\
\end{skillgroup}


\end{multicols}




\subsection{Other}
\begin{multicols}{3}
\begin{skillgroup}{Front-end}
\skill{Javascript}{3}
\skill{AngularJS}{2}
\skill{jQuery}{2}
\skill{JSF, Primefaces}{2}
\skill{HTML}{2}
\skill{CSS}{2}
\skill{Jasmine}{2}
\skill{Geb}{2}
\skill{Sahi}{2}
\end{skillgroup}

\begin{skillgroup}{Languages}
\skill{C++ 11}{2}
\skill{C\#}{2}
\skill{PHP}{2}
\skill{VB.NET}{2}
\skill{Groovy}{2}
\skill{Python}{2}
\skill{Prolog}{2}
\skill{Haskell}{2}
\skill{Matlab}{2}
\end{skillgroup}

\begin{skillgroup}{Graphics}
\skill{OpenGL}{2}
\skill{Vulkan}{1}
\skill{OpenCL}{2}
\skill{Oculus SDK}{2}
\skill{CMake}{2}
~\\
~\\
~\\
~\\
\end{skillgroup}

\end{multicols}

\begin{tabular}{r l}
$\ast$ & ~~ Limited, need to work under supervission\\
$\ast\ast$ & ~~ Autonomy on simple tasks, need couching for complex tasks\\
$\ast\ast$$\ast$ & ~~ Autonomy on complex tasks\\
$\ast\ast$$\ast\ast$ & ~~ Can lead, coach, supervise complex tasks
\end{tabular}

\addtolength{\oddsidemargin}{0cm}
\addtolength{\evensidemargin}{0cm}
\end{document}
